A Kochen-Specker system has at least 22 vectors

### 2015-05-11 paper/main.tex
typo
paper: remove superfluous "do"

\begin{definition}
Given a finite subset~$S$ of the projective plane
(or equivalently, a finite subset of the northern
hemisphere without equator\footnote{%
    A subset of the projective plane can be identified with
    a subset of the closed northern hemisphere.
    For a finite subset we can always rotate in such a way
    that no points lie on the equator.}).
Define its \keyword{orthogonality graph}~$G(S)$ as follows.
The vertices are the points of~$S$.
Two vertices are joined by an edge, if their corresponding points
are orthogonal.
\end{definition}
\begin{definition}
A graph~$G$ is called~\keyword{embeddable},
if it is as a subgraph of an orthogonality graph.
That is: if there is a finite subset~$S$ of the projective plane,
such that~$G \leq G(S)$.
\end{definition}
% TODO add remark on subgraph definition?
\begin{definition}
A graph is called~\keyword{010-colorable}
if there is a~$\{0,1\}$-coloring of the vertices,
with
\begin{enumerate}
\item
for each triangle there is exactly one vertex that is colored~$1$ and
\item
adjacent vertices are not both colored~$1$.
\end{enumerate}
\end{definition}

@@

This is the subgraph and we have given the vertices names corresponding
to the original, 19 vertex, graph. Below each name is a coordinate
on the sphere (whenever there is a $\cdot$ in the coordinate, we
mean that this component of the coordinate is fixed by the other
components, as it must be a point on the sphere, where we do take
this $\cdot$ to be the positive square root).

>>>>

\begin{definition}
Given a finite subset~$S$ of the projective plane
(or equivalently, a finite subset of the northern
hemisphere without equator\footnote{%
    A subset of the projective plane can be identified with
    a subset of the closed northern hemisphere.
    For a finite subset we can always rotate in such a way
    that no points lie on the equator.}).
Define its \keyword{orthogonality graph}~$G(S)$ as follows.
The vertices are the points of~$S$.
Two vertices are joined by an edge, if their corresponding points
are orthogonal.
\end{definition}
\begin{definition}
A graph~$G$ is called~\keyword{embeddable},
if it is a subgraph of an orthogonality graph.
That is: if there is a finite subset~$S$ of the projective plane,
such that~$G \leq G(S)$.
\end{definition}
% TODO add remark on subgraph definition?
\begin{definition}
A graph is called~\keyword{010-colorable}
if there is a~$\{0,1\}$-coloring of the vertices,
with
\begin{enumerate}
\item
for each triangle there is exactly one vertex that is colored~$1$ and
\item
adjacent vertices are not both colored~$1$.
\end{enumerate}
\end{definition}

@@

This is the subgraph and we have given the vertices names corresponding
to the original, 19 vertex, graph. Below each name is a coordinate
on the sphere (whenever there is a $\cdot$ in the coordinate, we
mean that this component of the coordinate is fixed by the other
components, as it must be a point on the sphere, where we take
this $\cdot$ to be the positive square root).
